Practical Optional Types for Clojure

### 2015-02-28 overview.tex
sub
egref

Here is the above program in Typed Clojure.

\begin{exmp}
\inputminted[firstline=1]{clojure}{code/demo/src/demo/eg1.clj}
\label{example:conditionalflow}
\end{exmp}

@@

Typed Clojure disallows reflection in typed code
so we must add back the type hint to obtain a well-typed
expression.

\begin{exmp}
\inputminted[firstline=10,lastline=10]{clojure}{code/demo/src/demo/parent3.clj}
\end{exmp}

@@

We include the above sequence of definitions as example~\ref{example:rep}.

@@

\paragraph{HMap dispatch} The flexibility of \clj{isa?} is key to the generality of multimethods. 
In example~\ref{example:incmap} we
dispatch on the \clj{:op} key 
of our HMap AST \clj{Expr}.
Since keywords are functions that look themselves up in their argument, we simply
use \clj{:op} as the dispatch function.

@@

\clj{inc-map} is like example~\ref{example:decmap} except the nodes are incremented.
The reasoning is similar, except we only consider one branch (the current method) by
locally considering the current \emph{dispatch value} and reasoning about how it relates
to the \emph{dispatch function}.
For example, 
in the \clj{:do} method we learn the \clj{:op} key is a \clj{:do}, which
narrows our argument type to the \clj{:do} Expr, and similarly for the \clj{:if}
and \clj{:const} methods.

@@

Example~\ref{example:multidispatch}
simulates multiple dispatch by dispatching on
a vector containing the class of both arguments. \clj{open}
takes two arguments which can be strings or files and returns
a new file that concatenates their paths.

We call three different \clj{File} constructors, each known at compile-time
via type hints.
Multiple dispatch follows the same kind of reasoning as example~\ref{example:incmap},
except we update multiple bindings simultaneously.

@@

Example~\ref{example:final}
combines everything we will cover for the rest of the paper:
multimethod dispatch, reflection resolution via type hints, Java method
and constructor calls, conditional and exceptional flow reasoning,
and HMaps.

>>>>

\newpage
Here is the above program in Typed Clojure.
\begin{exmp}
\inputminted[firstline=1]{clojure}{code/demo/src/demo/eg1.clj}
\label{example:conditionalflow}
\end{exmp}

@@

Typed Clojure disallows reflection in typed code
so we must add back the type hint to obtain a well-typed
expression.
\newpage
\begin{exmp}
\inputminted[firstline=10,lastline=10]{clojure}{code/demo/src/demo/parent3.clj}
\end{exmp}

@@

We include the above sequence of definitions as \egref{example:rep}.

@@

\paragraph{HMap dispatch} The flexibility of \clj{isa?} is key to the generality of multimethods. 
In \egref{example:incmap} we
dispatch on the \clj{:op} key 
of our HMap AST \clj{Expr}.
Since keywords are functions that look themselves up in their argument, we simply
use \clj{:op} as the dispatch function.

@@

\clj{inc-map} is like \egref{example:decmap} except the nodes are incremented.
The reasoning is similar, except we only consider one branch (the current method) by
locally considering the current \emph{dispatch value} and reasoning about how it relates
to the \emph{dispatch function}.
For example, 
in the \clj{:do} method we learn the \clj{:op} key is a \clj{:do}, which
narrows our argument type to the \clj{:do} Expr, and similarly for the \clj{:if}
and \clj{:const} methods.

@@

\egref{example:multidispatch}
simulates multiple dispatch by dispatching on
a vector containing the class of both arguments. \clj{open}
takes two arguments which can be strings or files and returns
a new file that concatenates their paths.

We call three different \clj{File} constructors, each known at compile-time
via type hints.
Multiple dispatch follows the same kind of reasoning as \egref{example:incmap},
except we update multiple bindings simultaneously.

@@

\egref{example:final}
combines everything we will cover for the rest of the paper:
multimethod dispatch, reflection resolution via type hints, Java method
and constructor calls, conditional and exceptional flow reasoning,
and HMaps.
